Where is the Context for Disambiguation? An Experimental Analysis.

### 2013-10-11 draft.tex
Versão atual da Carolina

@@

@@

@@

>>>>

This papers presents an experimental analysis of the impact of importing context information from different ontologies such as DBpedia in the recognition and semantic disambiguation of concepts and entities extracted from well known knowledge bases. We strongly believe that some type of context  of certain phrases support  a better disambiguation. Through this paper we aim to provide an efficient way to extract context in order to improve the disambiguation of named entities. We show that the process of  indexing context (...)

The DBpedia Spotlight process the linking of unstructured information sources to the Linked Open Data cloud through DBpedia, by automatically annotating mentions of DBpedia resources. It is able to recognize(...). Is also 
offers many potential sources of context to model each entity, such as title, sentence, paragraph, content, anchor, and so on. Through the contextual information extraction process for the disambiguation process, as well as the 
indexing of named entities among candidates entities of unstructured texts, the experimental analysis shows a higher disambiguation  accuracy in comparison with other research on Wikipedia resource.

DBpedia Spotlight relies on a number of data sources in order to support annotation tasks. Some sources provide metadata such as the types of entity: Person, Location or Organization, for instance. Other sources provide statistical context in which certain words are more strongly associated with certain entities. Thus, this analysis will allow us to  evaluate which sources of information provide best information for disambiguation.

---------------------

@@

\section{Resources}
\subsection{DBpedia}
\subsection{DBpedia Spotlight}
\section{Context Extraction}
The context extraction itself consists of processing the properties, objects, types and labels of the DBpedia resource and group them by the subject in order to have  different sources of context to model each DBpedia entity.
The very first step of such process is to extract all properties , objects and types of DBpedia resources. We consider as potential resources data provided by (1) the Mapping-based properties, as (...), (2) Instance types, as (...) and (3) wikilinks, in which (...). Each context is extracted individually, tokenized and then counted. In the next step, we used the DBpedia Spotlight extraction framework in order to obtain paragraphs from Wikipedias database and theirs corresponding DBpedias resources. From such paragraphs, we striped down words, entities, and so on in order to build an context from the neighborhood. [replace sentence]

\section{Context Indexing}

@@

In order to measure the impact of the proposed disambiguation technique, we carried out  (...)X evaluation of the context indexing. To this end, we have indexed data from several sources to run distinct automatic evaluation in choosing the correct candidate named entity for a given mention in the text. For the indexing purpose, we used the Dbpedia Spotlight extraction framework, in which we could analyze different scenarios from different context indexing (..). In such process, we were able to compare each individual result against each other, and also run a machine learning algorithm by combining individual context indexing. (...)

----------------

@@

\section{Results}

We will run the evaluation classes to test which of the methods for context extraction give better disambiguation results. We will also try to combine all of them to see if that performs better than each individual option. Finally, we can see which combinations offer best performance. This can be done by simply concatenating two-three datasets, or more smartly via machine learning. Each dataset provides one score and we use a machine learning algorithm to learn how to combine these scores into one such that disambiguation accuracy is maximized.
